Simulations of Ballot Polling Risk-Limiting Audits

### 2022-10-11 providence/sections/pilot.tex
providence numbers

>>>>

\begin{figure}
\includegraphics[width=.5\textwidth]{pilot_sims.png}
\caption{The total number of ballots sampled on average in our simulations of audits using the same contest parameters and risk limit as the pilot audit. The average total ballots are shown for various round schedules for which we ran simulations, parameterized by $p$ the conditional stopping probability used to select each round size.}
\label{fig:pilot_sims}
\end{figure}
